Concurrent Programming with CXL

### 2020-06-29 book/paper.tex
Added acknowledgments

\newpage
\printindex

\newpage
\printglossaries

>>>>

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgments}

I received considerable help and inspiration from various people
while writing this book.

First and foremost I would like to think my student Haobin Ni with
whom I've had numerous discussions about the design of CXL.
Haobin even contributed some code to the CXL compiler.

Most of what I know about concurrent programming I learned from
my colleague Fred Schneider.  He suggested I write this book after
demonstrating CXL to him.

Leslie Lamport introduced me to using model checking to test properties
of a concurrent system.  My experimentation with using TLC on Peterson's
Algorithm became an aha momment for me.

I first demonstrated CXL to the students in my CS6480 class on systems
and formal verification and
received valuable feedback from them.

I would also like to thank my proofreaders Anneke van Renesse and
Zhuoyu Xu.

Finally, I would like to thank my family who had to suffer as I obsessed
over writing the code and the book.

% I wrote the CXL compiler and this book in May and June of 2020,
% during the pandemic and the George Floyd demonstrations.

\cleardoublepage
\phantomsection
\printindex

\cleardoublepage
\phantomsection
\printglossaries
